Harmony: A Verifiable Systems Programming Language

### 2022-01-16 paper/paper.tex
Fixed interrupt handling

\emph{Charm}, Harmony's concurrent model checker, is an explicit state model
checker that computes a \emph{Kripke structure} (essentially, a graph)
of states reachable
from the initial state in a breadth-first manner, stopping only if
it encounters an error (such as divide-by-zero or a failing assertion)
or until there are no more new states.

@@

A data race occurs when two or more threads simultaneously try to
access the same shared data location, at least one of which is a
\texttt{Store}, \texttt{Stop}, or \texttt{Del} instruction.  Harmony
only considers this a problem it at least one of those threads is
not in atomic mode.  After all, we do not want to consider accesses
to a spinlock as a problem.  Also, the Harmony language allows
shared variables to be tagged as \emph{sequentially consistent},
effectively turning off data race detection.  Charm maintains on
each edge of the Kripke structure a list of accesses that were made
during the transition.  After all transitions from a state have been
computed, Charm checks for data races.

>>>>

\emph{Charm}, Harmony's concurrent model checker, is an explicit state model
checker that computes a \emph{Kripke structure}~\cite{Kripke1963}
(essentially, a graph) of states reachable
from the initial state in a breadth-first manner, stopping only if
it encounters an error (such as divide-by-zero or a failing assertion)
or until there are no more new states.

@@

A data race occurs when two or more threads simultaneously try to
access the same shared data location, at least one of which is a
\texttt{Store}, \texttt{Stop}, or \texttt{Del} instruction.  Data races
can also occur in a single thread that experiences an interrupt.  Harmony
only considers this a problem it at least one of those threads is
not in atomic mode.  After all, we do not want to consider accesses
to a spinlock as a problem.  Also, the Harmony language allows
shared variables to be tagged as \emph{sequentially consistent},
effectively turning off data race detection.  Charm maintains on
each edge of the Kripke structure a list of accesses that were made
during the transition.  After all transitions from a state have been
computed, Charm checks for data races.
